Appendix

### 2018-06-11 figures/06_k.Rmd
cleanup iws nws gis ex

k_viz_nws <- ggplot(
  fit_df_nws, 
  aes(x = coef, y = key, fill = key, color = key)) + 
  geom_density_ridges(size = 0.1, rel_min_height = 0.03, scale = 1) + 
  scale_fill_manual(values = c("grey",
                               rep(c(viridis::viridis(1, begin = 0.5),
                                     viridis::viridis(1, begin = 0)), 8))) +
  scale_color_manual(values = c("grey", 
                               rep(c(viridis::viridis(1, begin = 0.5), 
                                     viridis::viridis(1, begin = 0)), 8))) +
  cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
                                   axis.title = element_text(size = 12),
                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
                                   axis.line.x = element_line(size = 1, 
                                                  colour = "black"),
                                   axis.line.y = element_line(size = 1, 
                                                  colour = "black"), 
                                   legend.position = "none", 
                                   plot.margin = margin(0.5,0,0,-0.7, "cm")) + 
  xlab("Coefficient Value") +  ylab("") +
  scale_y_discrete(breaks = levels(fit_df_nws$key)[
    c(1, seq(3, length(levels(fit_df_nws$key)), by = 2))], 
    labels = rev(c("Link length",
                   "Closest lake distance",
                   "Stream density",
                   "Lake connection", 
                   "Max depth",
                   "Baseflow",
                   "Stream order ratio",
                   "Global")))

>>>>

k_viz_nws <- ggplot(
  fit_df_nws, 
  aes(x = coef, y = key, fill = key, color = key)) + 
  geom_density_ridges(size = 0.1, scale = 1) + 
  scale_fill_manual(values = c("grey",
                               rep(c(viridis::viridis(1, begin = 0.5),
                                     viridis::viridis(1, begin = 0)), 8))) +
  scale_color_manual(values = c("grey", 
                               rep(c(viridis::viridis(1, begin = 0.5), 
                                     viridis::viridis(1, begin = 0)), 8))) +
  cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
                                   axis.title = element_text(size = 12),
                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
                                   axis.line.x = element_line(size = 1, 
                                                  colour = "black"),
                                   axis.line.y = element_line(size = 1, 
                                                  colour = "black"), 
                                   legend.position = "none", 
                                   plot.margin = margin(0.5,0,0,-0.7, "cm")) + 
  xlab("Coefficient Value") +  ylab("") +
  scale_y_discrete(breaks = levels(fit_df_nws$key)[
    c(1, seq(3, length(levels(fit_df_nws$key)), by = 2))], 
    labels = rev(c("Link length",
                   "Closest lake distance",
                   "Stream density",
                   "Lake connection", 
                   "Max depth",
                   "Baseflow",
                   "Stream order ratio",
                   "Global")))

### 2018-06-11 manuscript/appendix.Rmd
cleanup iws nws gis ex

```{r load_packages}

@@

```{r source_functions}

@@

```{r iws_vs_nws-gis, cache = TRUE, echo=FALSE}
# lagoslakeid <- 6302
# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
# focal_lake <- 
# upstream_lakes <- 
# saveRDS(iws, "../data/iws_extent.rds")
# saveRDS(nws, "../data/nws_extent.rds")

@@

ggplot() + 
  geom_sf(data = nws_outline, color = "cyan", size = 2) + 
  geom_sf(data = iws_outline, color = "cyan", size = 1, linetype = "dashed") + 
  geom_sf(data = nws) +
  # geom_sf(data = iws) + 
  theme_void()

@@

                           ggplot() + 
                             geom_sf(data = us_states) +
                             geom_sf(data = nes_sf, 
                                     color = viridis::viridis(1, begin = 0),
                                     size = 1) + 
                             geom_sf(data = nes_sub,
                                     color = viridis::viridis(1, begin = 0.5), 
                                     size = 1) + 
                             coord_sf(datum = NA) + 
                             ggtitle(break_word(partition_splits[x, "abb"], 12)) + 
                             theme(plot.margin = unit(c(0, -0.1, 0, -0.1), "cm"), 
                               plot.title = element_text(face = "plain", size  = 12))
                         })

>>>>

```{r load_packages, echo=FALSE}

@@

```{r source_functions, echo=FALSE}

@@

```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE}
# lagoslakeid <- 6302
# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
# focal_lake <- 
# upstream_lakes <- 
# saveRDS(iws, "../data/iws_extent.rds")
# saveRDS(nws, "../data/nws_extent.rds")

@@

ggplot() + 
  geom_sf(data = nws_outline, color = "yellow", size = 2) + 
  geom_sf(data = iws_outline, color = "cyan", size = 2) + 
  geom_sf(data = nws) +
  coord_sf(crs = st_crs(nws), datum = NA) + 
  # geom_sf(data = iws) + 
  theme_void()

@@

                           ggplot() + 
                             geom_sf(data = us_states) +
                             geom_sf(data = nes_sf, 
                                     color = viridis::viridis(1, begin = 0),
                                     size = 1.4) + 
                             geom_sf(data = nes_sub,
                                     color = viridis::viridis(1, begin = 0.5), 
                                     size = 1) + 
                             coord_sf(datum = NA) + 
                             ggtitle(break_word(partition_splits[x, "abb"], 12)) + 
                             theme(plot.margin = unit(c(0, -0.1, 0, -0.1), "cm"), 
                               plot.title = element_text(face = "plain", size  = 12))
                         })
